Supporting Information

### 2016-11-29 code/rmarkdown/cover-letter.tex
+ fix typo in cover letter
+ remove the github repo from the cover letter because this will be made available once the repo has been accepted

We chose to publish our work in \textit{Methods in Ecology and Evolution} because of its focus on novel statistical and computational methodologies. We desire to communicate our findings to the global community of ecologists and conservation biologists that follow this journal. The content of our manuscript has not been published elsewhere has not been published elsewhere, nor has it been submitted for publication to another journal. All authors approved the manuscript and this submission. In support of the journal's commitment to reproducible research, we have stored all data, code, and results in an online repository to permit replication and validation of this study (\url{https://www.github.com/jeffreyhanson/raptr-manuscript}).

>>>>

We chose to publish our work in \textit{Methods in Ecology and Evolution} because of its focus on novel statistical and computational methodologies. We desire to communicate our findings to the global community of ecologists and conservation biologists that follow this journal. The content of our manuscript has not been published elsewhere, nor has it been submitted for publication to another journal. All authors approved the manuscript and this submission.
